---
output:
  knitrBootstrap::bootstrap_document:
title: "ANA 515 Assignment 1"
theme: slate
author: "Emily Zhao"
date: "2022"



---

```{r setup, include = TRUE}
#The include = FALSE function hides both the code and output in my output document

#You need to install these packages first to be able to use the functions within them. You can install them from the Tools tab or write a new code chunk: install.packages("package_name"). 

#install.packages("tidyverse")
#install.packages("knitr")
#install.packages("bslib")

#library(devtools)
#install_github('rstudio/rmarkdown')
#install.packages('knitr', repos = c('http://rforge.net', 'http://cran.rstudio.org'),
                # type = 'source')
#install_github('jimhester/knitrBootstrap')
#library(rmarkdown)
library(knitrBootstrap)



```

4.	code chunk to get the dataset from GitHub/fivethirtyeight

``` {r, include = TRUE}
url <- "https://raw.githubusercontent.com/fivethirtyeight/guns-data/master/full_data.csv"
library(tidyverse)
#library(knitr)
library(bslib)
library(ggplot2)
library(dplyr)
gun <- read_csv(url)
glimpse(gun)


```
5.	code chunk to create a subset of gun_deaths
a.	Call the installed packages
b.	create a new dataset with the name of ‘youth’ from the dataset ‘gun_deaths’ that filters gun_deaths by 
age <= 65


``` {r, include = TRUE}
#a
library(tidyverse)
#library(knitr)
library(bslib)
library(ggplot2)
library(dplyr)

#b
youth<-gun%>%filter(age<=65)


```
7.	Write inline code that says:
##`We have data about 100798 individuals killed by guns. Only 15687 are older than 65.` 

```{r, include = TRUE}
nrow(gun)-nrow(youth)

```

8.	Code chunk to graph the distribution of the age variable from the youth dataset:
Use the ggplot function:
```{r, include = TRUE}
youth%>%
ggplot(aes(age))+
geom_freqpoly(binwidth=1)

```
9.	Code chunk to graph the distribution of youth by race
```{r, include = TRUE}
#Once all of my code has been written, I click on the Knit button in the tool bar above to produce my document.
youth %>% 
ggplot(aes(fct_infreq(race) %>% fct_rev())) + 
geom_bar() + coord_flip() + 
labs(x = "Victim race") 


```
